Notes and approaches to OCR

### 2020-12-03 outputs/documents/paper.Rmd
Text cleaning

For the purpose of this study, one page from the letter a in the Japanese dictionary was taken to assess the selected OCR tools. This image contains 3293 characters. Words in English were counted as one character for this analysis. MOreover, the sample text was divided into four images called **sections** as it is illustrated in figure XX. These new images were assessed across all OCR tools.

@@

This example is in a vertical form, meaning that it should be read it from right to left and from the top to the bottom. This is important since it is expected to obtain from each OCR tool the correct sequence of characters. FOr instance, from section 1 in figure xx, the first five characters from the first line are **[一本の傘を]**

@@

Among the Microsoft Azure's portfolio, Azure Cognitive Services offers Computer Vision, an API that processes images and returns information based on the visual features the user is interested in. Those services comprise object detection of an image, visual features tagging, image categorization, Optical Character Recognition (OCR), among $others^4$. The OCR API processes an image and returns the language of the document, orientation, regions, lines, and finally, the characters.

@@

Figure 1 presents a sample that corresponds to the section 1 of the image containing Japanese text, but it also contains English text in some fragments of the text. The API offers the possibility to do self-detection, which in this case is helpful, but also the opportunity to specify the language in advance. Moreover, the orientation can also be self-detected or not.

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/azure-images/section1.png)
**Figure 1**

@@

The blue line figure 2 denotes the segment from the image that includes the characters. In this example, there is only one blue line because the document is only text. In other cases, it may contain images requiring more than one region.

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/azure-images/region-section1.png)
 **Figure 2**

@@

Once the region is defined, the API provides in figure 3 (red rectangles) the subsets of characters of the region called Lines. From the example, we can see that some characters are not included in any of the lines. Those characters are not recognized by the API.

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/azure-images/lines-section1.png)   
 **Figure 3**

@@

After the lines are identified, the API provides in figure 4 each recognized character bounding boxes. Those without a yellow square were not recognized by the API in this example.

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/azure-images/boundaries-section1.png)
 **Figure 4**

@@

Once the bounding boxes are located, each character takes its corresponding place, as it is shown in figure 5.

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/azure-images/characters-section1.png)
 **Figure 5**

@@

Even though the API offers the possibility to self-detect the language, It changes the order in which the characters should be in the output. In figures 6 we can see that the first line provided by the self-detection approach is located in the middle. This situation does not allow a correct interpretation of the text because it does not follow the reading pattern. In this case, it is a vertical orientation, which means we have to read it from right to left.

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/azure-images/self-detection.png)
 **Figure 6**

When the parameter language is stated as Japanese since the beginning, as we can see in figure 7, it recognizes the first line correctly.

@@

The following example illustrates how to state the headers and parameter, but also create two functions. The first one, called encode_image converts an image into base64, an encoding process designed to carry data stored in binary formats across channels that only reliably support text content. It can embed image files or other binary assets inside textual assets. The second one makes an HTTP POST request that calls Google's Vision API.

@@

From the previous example, we can observe that the response returns a list of nested dictionaries. The first nested dictionary called **textAnnotations** consists of a list of nested dictionaries. Each one of those has a description (character) and boundingPoly (boundaries of the characters).

@@

Figure 8 shows the region identified by the API.

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/google-images/sections.png)
 **Figure 8**

@@

The remaining objects enclose the boundaries of the characters. As it is shown in figure 9, each boundingPoly node can include one or more characters.

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/google-images/boundaries.png)
**Figure 9**

@@

Once the bounding boxes are located, each character takes its corresponding place, as it is shown in figure 10. **Pending find a way to plot the text in vertical form to make it readable.**

@@

**Figure 10**

@@

Google Vision API offers the advantage of including in the request language hints. It consists of a list of languages the user knows in advance the image contains. For this study, we run two versions, one without hints and the other one with a list of two hints, such as Japanese and English, as the image contains some words in English.

@@

>>>>

For the purpose of this study, one page from the letter a in the Japanese dictionary was taken to assess the selected OCR tools. The image contains 3293 characters. Words in English were counted as one character for this analysis. MOreover, the sample text was divided into four images called **sections** as it is illustrated in figure XX. These new images were assessed across all OCR tools.

@@

This example is in a vertical form, meaning that it should be read it from right to left and from the top to the bottom. This is important since it is expected to obtain from each OCR tool the correct sequence of characters. For instance, from section 1 in figure xx, the first five characters from the first line are **[一本の傘を]**. We expect to see the same sequence from each OCR tool.

@@

Among the Microsoft Azure's portfolio, Azure Cognitive Services offers Computer Vision, an API that processes images and returns information based on the visual features the user is interested in. Those services comprise object detection of an image, visual features tagging, image categorization, Optical Character Recognition (OCR), among $others^4$. The OCR API processes an image and returns the language of the document, orientation, regions, lines, boundaries, and finally, the characters.

@@

Figure xx presents a sample that corresponds to the section 1 of the image containing Japanese text, but it also includes English text in some fragments of the text. The API offers the possibility to do self-detection, which in this case is helpful, but also the opportunity to specify the language in advance. Moreover, the orientation can also be self-detected or not.

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/azure-images/section1.png)
**Figure xx**

@@

The blue line figure xx denotes the segment from the image that includes the characters. In this example, there is only one blue line because the document is only text. In other cases, it may contain images requiring more than one region.

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/azure-images/region-section1.png)
 **Figure xx**

@@

Once the region is defined, the API provides in figure xx (red rectangles) the subsets of characters of the region called Lines. From the example, we can see that some characters are not included in any of the lines. Those characters are not recognized by the API.

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/azure-images/lines-section1.png)   
 **Figure xx**

@@

After the lines are identified, the API provides in figure xx each recognized character bounding boxes (yellow regions). Those without a yellow square were not recognized by the API in this example.

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/azure-images/boundaries-section1.png)
 **Figure xx**

@@

Once the bounding boxes are located, each character takes its corresponding place, as it is shown in figure xx.

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/azure-images/characters-section1.png)
 **Figure xx**

@@

Even though the API offers the possibility to self-detect the language, It changes the order in which the characters should be in the output. In figure xx we can see that the first line provided by the self-detection approach is located in the middle. This situation does not allow a correct interpretation of the text because it does not follow the reading pattern. In this case, it is a vertical orientation, which means we have to read it from right to left.

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/azure-images/self-detection.png)
 **Figure xx**

When the parameter language is stated as Japanese since the beginning, as we can observe in figure xx, it recognizes the first line correctly.

@@

The following example illustrates how to state the headers and parameter, but also create two functions. The first one, called encode_image converts an image into base64 format, an encoding process designed to carry data stored in binary formats across channels that only reliably support text content. It can embed image files or other binary assets inside textual assets. The second one makes an HTTP POST request that calls Google's Vision API.

@@

From the previous example, we can observe that the response returns a list of nested dictionaries. The first nested dictionary called **textAnnotations** consists of a list of dictionaries. Each one of those has a description (character) and boundingPoly (boundaries of the characters).

@@

Figure xx shows the region identified by the API.

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/google-images/sections.png)
 **Figure xx**

@@

The remaining objects enclose the boundaries of the characters. As it is shown in figure xx, each boundingPoly node can include one or more characters.

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/google-images/boundaries.png)
**Figure xx**

@@

Once the bounding boxes are located, each character takes its corresponding place, as it is shown in figure xx. **Pending find a way to plot the text in vertical form to make it readable.**

@@

**Figure xx**

@@

Google Vision API offers the advantage of including in the request language hints. It consists of a list of languages the user knows in advance the image contains. For this study, we run two versions, one without hints and the other one with a list of two hints, such as Japanese and English, as the image contains some words in English. Both versions returned the same output.

@@

Unlike Azure Cognitive Services, which returns each recognized character individually, Google Vision groups characters in some cases. This situation adds some degree of complexity when processin the response from the API. **[Not sure if it is a disadvantage in real life]**
